Predictive analytics in quality assurance for assembly processes: lessons learned from a case study at an industry 4.0 demonstration cell

### 2020-11-03 02_Paper/paper.tex
robot arm figure.

\section{The case industry 4.0 demonstration cell} % (taken from title) % 3/4 Page \OneAim doc bases
\begin{figure}
       \includestandalone[width=.45\textwidth]{img/cell_data_plot}
       \caption{Robot arm movement patterns.}
\end{figure}

@@

\subsection{Machine Learning}

@@

\subsection{Classifier optimization and testing}
We work with a total of 132 measurements. Each containing arm and belt data
logs of individual cell runs. 20 samples are set aside at random for testing 
purposes, leaving 112 training samples. The random number generator seed is
set to one in order to ensure the train and test set splits are identical 
for all experiments.

@@

>>>>

\section{The case industry 4.0 demonstration cell} % (taken from title) % 3/4 Page \OneAim doc bases
\begin{figure}
\caption{The industry simulation cell. \MW{TODO: Find image.}}
\label{fig:ind_cell}
\end{figure}

\begin{figure}
       \includestandalone[width=.45\textwidth]{img/arm_data_plot}
       \caption{Robot arm movement patterns. We show the movement of the 
                cell's robot arm, its grippers and an encoding of the overall
                position in the system. The changes in the grip flag are triggered,
                when the gripper opens or closes. Zero indicates an open, while
                one indicates a closed gripper. The position flags marks the state
                of the cell's arm.  0 means the black disk is in store,
                one that the black disk is in the gate, two that the white disk
                is in store and three that the white disk is located in gate.
             }
\label{fig:robot_pos_cell}
\end{figure}

@@

\subsection{Machine Learning}
We compare Support Vector Machines (SVM), Multilinear Perceptrons
\cite{bishop2006pattern} as well as Random forests in the task of
quality prediction.

@@

\subsection{Classifier optimization and testing}\label{sec:ml_exp}
The robot's position at disc drop is marked in 
Figure~\ref{fig:robot_pos_cell}. The quality prediction problem is 
framed as a classification task. The input vectors which we feed into our
classifiers consists of the arm positions at the disc drops for both
discs in three dimensions, as well as the largest recorded belt speed
of all three belts. The interpretation of the quality measurement is 
used as the training target. It can be good or bad which we encode as 
zero and one.

We work with a total of 132 measurements. Each containing arm and belt data
logs of individual cell runs. 20 samples are set aside at random for testing 
purposes, leaving 112 training samples. The random number generator seed is
set to one in order to ensure the train and test set splits are identical 
for all experiments.

@@

\bibliographystyle{abbrv}
\bibliography{bib}
